{Gravitational wave sources in our Galactic backyard:}\\{Predictions for BHBH, BHNS and NSNS binaries detectable with LISA

### 2022-03-17 paper/tex/sections/introduction.tex

One particularly interesting class of potential LISA sources is BHNSs. With the recent detection of two BHNSs by the LIGO scientific collaboration, the existence of these DCOs has been confirmed \citep{TheLIGOScientificCollaboration+2021}. However, with only two detections (not including the low-confidence candidate GW190426, \citealt{Abbott+2020_GWTC2}, or GW190425, GW190814 and GW190917 which have not been ruled out as BHNSs, \citealt{Abbott+2020_GW190425,Abbott+2020_GW190814, GWTC_2_1}) and no electromagnetic counterparts, the formation rate and properties of BHNSs are still uncertain. Similar to NSNSs, these binaries are also expected to have electromagnetic counterparts. A distinctly exciting possibility is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991, Pol+2021}. These systems could be observed not only by LISA, but also radio telescopes such as MeerKAT and the Square Kilometre Array (SKA, \citealt{Dewdney+2009}), which would help to improve the measurement of individual system parameters and to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}.

>>>>

One particularly interesting class of potential LISA sources is BHNSs. With the recent detection of two BHNSs by the LIGO scientific collaboration, the existence of these DCOs has been confirmed \citep{TheLIGOScientificCollaboration+2021}. However, with only two detections (not including the low-confidence candidate GW190426, \citealt{Abbott+2020_GWTC2}, or GW190425, GW190814 and GW190917 which have not been ruled out as BHNSs, \citealt{Abbott+2020_GW190425,Abbott+2020_GW190814, GWTC_2_1}) and no electromagnetic counterparts, the formation rate and properties of BHNSs are still uncertain. A distinctly exciting possibility for BHNSs is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991, Pol+2021}. These systems could be observed not only by LISA, but also radio telescopes such as MeerKAT and the Square Kilometre Array (SKA, \citealt{Dewdney+2009}), which would help to improve the measurement of individual system parameters and to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}. \edit1{Moreover, the pulsar acts as an ultraprecise clock around a BH and thus a pulsar--BH system provides stringent tests of theories of gravity \citep{Keane+2015}.}
